Motional Quantum Ground-State Cooing Outside the Lamb-Dicke Regime

### 2017-06-23 paper.tex
Edits from Nick

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}

@@

\begin{abstract}
  Single neutral atom trapped in optical tweezer is a promising system for various applications
  in quantum information and simulation.
  The control of the motional states for such a system is crucial
  for exploiting its full potential.
  We report Raman sideband cooling of a single sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite having a very large Lamb-Dicke parameter, high initial temperature and
  large differential AC Stark shift in the excited state,
  we achieved a ground state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling
  by using a few new cooling techniques including addressing high order Raman sideband.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable to
  systems where tight confinement or low initial cooling is hard to achieve.
  The is particularly relevant for systems which are challenging to laser-cool,
  such as molecules and exotic atoms, and opens up a new approach for further cooling
  of these systems.
\end{abstract}

@@

Systems of single neutral atoms trapped in optical tweezers are an exciting platform to study
quantum information, quantum chemistry, and quantum simulation of many-body systems \fxnote{REF}.
This approach provides full single-site resolution and control,
and can feature long-range interactions via Rydberg atoms, polar molecules,
or dipolar atoms \fxnote{REF}.
Polar molecules in particular offer the additional advantages of long-lived internal states
and a high degree of tunability, including the shape, range,
and strength of the interaction \fxnote{REF}.
Optical tweezers can also be re-arranged in real-time,
allowing rapid preparation of atoms in complex geometries with high fidelity \fxnote{REF}.

@@

The Raman sideband cooling we used to achieve the high ground state preparation fidelity
consists of multiple cycles of laser pulses to manipulate the internal and
motional states of the atoms.
Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
in our setup.
Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
ground electronic state and a certain vibration state $n$.
In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
In the second step, which finishes the cooling cycle,
an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
the entropy.
The second step could also change the motional state of the atoms which could cause heating.
The possibility for this to happen for an atom in the motional level $n$
is approximately proportional to the effective Lamb-Dicke parameter
$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
is the Lamb-Dicke parameter for optical pumping.
Additional photon scattering on the atom in the $|F=2, m_F=-2\rangle$
state will also cause heating.
In order to reduce this effect, we address the atom in the $F=2$ states during optical pumping
on the D1 line, so that the $|F=2, m_F=-2\rangle$ state is a dark state for $\sigma^-$
polarization and does not scatter any photon. We measured a $130(20)$ times reduction in photon
scattering rate on $|F=2, m_F=-2\rangle$ state compare to using only the D2 line
with the same optical pumping rate.
The geometry of the relevant beams and their polarizations is showed in figure \ref{f-setup}B.
The optical tweezer has one weakly confined axial direction (axis $1$) and
two more strongly confined radial directions (axis $2$ and $3$).
Multiple pairs of beams are used to drive the Raman transition during cooling in order to
isolate and maximize the coupling to different trap axis.

In order to perform Raman sideband cooling efficiently and minimize
the heating during the optical pumping, we need to have a low initial temperature and
a small Lamb-Dicke parameter. However, since the Lamb-Dicke parameter $\eta$ is inversely
proportional to $\sqrt[4]{m}\lambda$ where $m$ is the mass of the atom and $\lambda$
is the wavelength of the atomic transition,
it is larger for sodium at a given trap depth due to its low mass and short D line wavelength.
With 45 mW of power in the trap, we measure trapping frequencies of
$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$
which corresponds to optical pumping Lamb-Dicke parameters of
$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$
Moreover, due to the small hyperfine structure in the $3^2P_{3/2}$ manifold,
the sub-Doppler cooling in sodium is also less efficient and we start the
Raman sideband cooling with a initial temperature of 70 $\mu$K. Combined with the high Lamb-Dicke
parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$
As a result, there is a very high probability of heating during the optical pumping step
(figure \ref{f-ld}B) causing an estimated $30\%$ average heating probability during optical pumping
in the weakly confined axial direction.

Fortunately, the high Lamb-Dicke parameters also
provide us with tools to overcome this issue. The Lamb-Dicke parameters for the
Raman transitions in our configuration are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$. As shown in
figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
of cooling sidebands, especially for high motional states.
This enables cooling of atoms in high motional states by driving higher order Raman sidebands,
removing more motional energy in a single cooling pulse and offsetting the effect of heating. Since the heating probability is higher for high motional states,
cooling on these high order sidebands can greatly suppress the high heating during
optical pumping during the initial cooling. Since the coupling strength of different orders
do not reach their minimums at the same time, using multiple orders of motional sidebands
for cooling also avoids accumulation of population near the coupling minimum of a particular
order, which improves the overall efficiency of the cooling process.

The high initial temperature also causes additional complications.
First, population in high motional states means that the atoms sample
the anharmonicity of the trap away from the harmonic center.
This effect broadens the sidebands and reduces their heights,
and therefore the efficiency of cooling, when driven with a single frequency.
In order to overcome this issue, we power broaden the sidebands by increasing the Rabi frequency
so that it is larger than the expected sideband frequencies distribution
which causes all the states to be driven equally.
This limits the Rabi frequency of the Raman pulse on the radial sidebands to be no lower
than tens of kHz.
Second, the deep trap that is needed to trap and image single sodium atom also creates
a very large AC Stark shift in the excited state (as large as 300 MHz).
This creates large, position-dependent detuning for the optical pumping light and mixes the excited state state hyperfine levels,
which affects the branching ratios and increases the number of photons needed for optical pumping.
We solve this issue by switching the trapping light at $3\text{MHz}$
during the whole cooling sequence, similar to our loading and imaging process
\cite{Hutzler2017-LightShifts}, but leave on the OP light with constant intensity.
Due to the large light shift, the OP light is effectively off when the trap light is on.
Since the atom can only be addressed by the optical pumping light when the trap light is off,
the effect of light shift on optical pumping fidelity is suppressed.

Taking all these features of our system into account, we use a Monte-Carlo simulation to verify
the validity of our method \fxnote{WRITE BRIEF SUMMARY IN APPENDIX?}.
In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
and confirm that by using high order Raman sideband transition in the cooling sequence we can
suppress this effect and reduces the motional energy of the atom faster.
The simulation is also used to guide the optimization of the cooling sequence by exploring the
large parameter space and finding a robust cooling strategy.
As shown in figure \ref{f-setup}C, we found that instead of cooling on only one sideband order
at a time, it is generally more efficient to alternate the cooling pulse between two
neighboring orders (axial) to minimize the accumulation of atom in a state
not addressed by a particular order.
The simulation also shows that the most efficient way of cooling on a high order sideband is
to perform a $\pi$ pulse corresponding to its maximum matrix element.
This makes sure we are using each order to cool a range of states that has the strongest
coupling to this order and let other sidebands to cool other states.
This strategy is only not as effective during the last stage of cooling in each direction
where most of the remainly excited population is in the first motional excited state
while the rest also have the strongest coupling to the first cooling sideband.
Because of this, we switch to cooling only on the first order sideband as the last cooling
stage while maintaining the alternating order between different axis to maximize the final
ground state probability.
Guided by the simulation result, we construct our initial cooling sequence by first starting
at the highest two observed cooling sideband and decrease the order after cooling on them
for 6 to 15 cycles with the optimum pulse lengths.
This sequence gives good cooling performance which is then experimentally further optimized
by fine tuning of different parameters.

For the more tightly confined radial directions,
we begin the cooling with $\{\bar n_2, \bar n_3\}=3.4(2), 2.5(2)$
The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
as orange and red lines, where we can clearly see the first order heating,
first order cooling and second order cooling sidebands.
After applying around 1000 cooling pulses cooling in all three dimensions
starting with cooling on the radial second order,
the Raman spectrum with the same parameters is shown in figure \ref{f-radial}A as
blue and green lines, where the first and second order cooling sidebands
on both axis are suppressed.
Given the absence of the second order cooling sideband,
we can estimate the ground state probability in each direction based on the height of
the first order cooling and heating sideband to be $90(2)\%$ and $94(3)\%$.

It is important to note that the large Raman Lamb-Dicke parameters $\eta^R$ mean that
we must use caution when measuring the temperature.
Traditional sideband thermometry uses
the ratio of the cooling and heating sidebands to measure $\bar n / (\bar n + 1)$, which relies
on the coupling strength to be proportional to $\sqrt{n}$. However, outside the
Lamb-Dicke regime, the coupling strength deviates from this simple scaling rule rapidly as
shown in figure \ref{f-ld}A.
When the atom temperature is still high,
we measure the heights of multiple sidebands to make sure no population is hidden at the
minimum of one sideband order. Once the atom is cooled down, we estimate the temperature
and ground state population under the assumption that only a few states are populated.
We can verify the result via an independent measurement of Rabi flopping on the carrier and heating
sidebands. This data is shown before and after cooling in Figures
\ref{f-radial}B and \ref{f-radial}C and yields $89(2)\%$ and $92(2)\%$
showing good agreement between the two methods.

The axial direction is much less confined and therefore has a much higher initial effective
Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx 4.0$, and is therefore more difficult to cool.
The red line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
before applying Raman sideband cooling; the clearly resolved sidebands
up to eighth order indicates population in highly-excited motional levels.
Therefore, we begin our cooling sequence by driving Raman transitions on the eighth order axial
cooling sideband. After applying the cooling sequence identical to the one we use to cool
the radial directions, the spectrum is shown in figure \ref{f-axial}A as the blue line.
All of the high order ($\geqslant2$) axial cooling sidebands disappear, and the first order
cooling sideband is strongly suppressed.
The ground state probability calculated from this spectrum is $92(3)\%$.
We can again use Rabi flopping on the carrier and heating sideband to verify this result
similar to the radial direction. In this case, we see very good agreement on the carrier
(figure \ref{f-axial}B) but there is additional decoherence on the axial first order
heating sideband (figure \ref{f-axial}C).
We believe this decoherence is caused by technical noise, which is the most pronounced
on this transition due to its slow Rabi frequency.
The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG that we have measured in the lab, which produces
a Zeeman shift of around $3$ kHz.

>>>>

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\eff}{ef\! f}
%Nick redefined fxnote so that the notes could be seen in the PDF since that is what Kang-Kuen is editing
\renewcommand{\fxnote}[1]{{\textbf{[#1]}}}

@@

\begin{abstract}
  Single neutral atoms trapped in optical tweezers are a promising system for many applications
  in quantum information and simulation.
  These applications typically require complete quantum control, including motional states, which requires cooling of the trapped atoms.
  We report Raman sideband cooling of a single sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite having a very large Lamb-Dicke parameter, high initial temperature and
  large differential AC Stark shift in the excited state,
  we achieve a ground state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling
  by using novel cooling techniques such as addressing high order Raman sidebands.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable outside the Lamb-Dicke regime, for example in
  systems where tight confinement and low initial temperature are difficult to realize.
  The is particularly relevant for systems which are challenging to laser-cool,
  such as molecules and exotic atoms, and opens up a new approach for further cooling
  of these systems.
\end{abstract}

@@

Systems of individual neutral atoms trapped in optical tweezers are an exciting platform to study
quantum information, quantum chemistry, and quantum simulation of many-body systems \fxnote{REF}.
This approach provides full single-site resolution and control,
and can feature long-range interactions by using Rydberg atoms, polar molecules,
or dipolar atoms \fxnote{REF}.
Polar molecules in particular offer the additional advantages of long-lived internal states
and a high degree of tunability, including the shape, range,
and strength of the interaction \fxnote{REF}.
Optical tweezers can also be re-arranged in real-time,
allowing rapid preparation of atoms in complex geometries with high fidelity \fxnote{REF}.

@@

The Raman sideband cooling we use to achieve the high ground state preparation fidelity
consists of multiple cycles of laser pulses to manipulate the internal and
motional states of the atoms.
Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
in our setup.
Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
ground electronic state and a certain vibration state $n$.
In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
In the second step, which finishes the cooling cycle,
an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
the entropy via the spontaneously emitted photon.
The second step could also change the motional state of the atoms and result in heating.
The possibility for this to happen for an atom in the motional level $n$
is approximately proportional to the effective Lamb-Dicke (LD) parameter
$\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
is the LD parameter for optical pumping, $k^{OP}$ is the wavenumber of the OP light, $m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.

In order to reduce OP scattering on the $|F=2, m_F=-2\rangle$ state, which would causing heating, we use a $\sigma^-$-polarized laser resonant with the D1 line to address atoms in the $F=2$ state, so that $|F=2, m_F=-2\rangle$ is dark.  Compared to using a D2 OP beam, we find a reduction in the scattering rate of a factor of $130(20)$.

The geometry of the relevant beams and their polarizations is shown in figure \ref{f-setup}B.
The optical tweezer has one weakly confined axial direction (axis $1$) and
two more strongly confined radial directions (axis $2$ and $3$).
Multiple pairs of beams are used to drive the Raman transition during cooling in order to
isolate and maximize the coupling to different trap axis.

In order to perform Raman sideband cooling efficiently and minimize
the heating during the optical pumping, we need to have a low initial temperature and
a small LD parameter. However, since the LD parameter $\eta\propto 1/(\sqrt[4]{m}\lambda)$ where $m$ is the mass of the atom and $\lambda$
is the wavelength of the atomic transition,
it is larger for sodium at a given trap depth due to its low mass and short D line wavelength.
With 45 mW of power in the trap, we measure trapping frequencies of
$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$
which corresponds to optical pumping LD parameters of
$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$
Moreover, due to the small hyperfine splitting in the $3^2P_{3/2}$ manifold,
the sub-Doppler cooling in sodium is also less efficient and we start the
Raman sideband cooling with a initial temperature of 70 $\mu$K. Combined with the high $\eta$, this gives us a initial effective optical pumping LD parameters of
$\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$
As a result, there is a very high probability of heating during the optical pumping step
(figure \ref{f-ld}B) causing an estimated $30\%$ average heating probability during optical pumping
in the weakly confined axial direction \fxnote{So what?  Is 30\% too high?  Can we interpret this in terms of an observable, like best-possible ground state fraction?}.

Fortunately, the high LD parameters also
provide us with tools to overcome this issue. The Raman transitions in our configuration have $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$. As shown in
figure \ref{f-ld}A, this results in strong coupling to higher orders
of cooling sidebands, especially for high motional states.
This enables cooling of atoms in high motional states by driving higher order Raman sidebands,
removing more motional energy in a single cooling pulse and offsetting the effect of heating. Since the heating probability is higher for high motional states,
cooling on these high order sidebands can greatly suppress the high heating during
optical pumping during the initial cooling. Since the coupling strength of different orders
do not reach their minimums at the same time, using multiple orders of motional sidebands
for cooling also avoids accumulation of population near the coupling minimum of a particular
order, which improves the overall efficiency of the cooling process.

The high initial temperature also causes additional complications beyond large $\eta$.
First, population in high motional states means that the atoms sample
the anharmonicity of the trap away from the harmonic center.
This effect broadens the sidebands and reduces their strengths on resonance,
and therefore the efficiency of cooling, when driven with a single frequency.
In order to overcome this issue, we power broaden the sidebands by increasing the Rabi frequency
so that it is larger than the expected sideband frequencies distribution
which causes all the states to be driven equally.
This limits the Rabi frequency of the Raman pulse on the radial sidebands to be no lower
than tens of kHz.
Second, the deep trap that is needed to trap and image single sodium atom also creates
a very large AC Stark shift in the excited state (as large as 300 MHz).
This creates large, position-dependent detuning for the optical pumping light and mixes the excited state state hyperfine levels,
which affects the branching ratios and increases the number of photons needed for optical pumping.
We solve this issue by switching the trapping light at 3 MHz
during the whole cooling sequence, similar to our loading and imaging process
\cite{Hutzler2017-LightShifts}, but leaving on the OP light with constant intensity.
Due to the large light shift, the OP light is effectively off when the trap light is on.
Since the atom can only be addressed by the optical pumping light when the trap light is off,
the effect of light shift on optical pumping fidelity is suppressed.

Taking all these features into account, we use a Monte-Carlo simulation to verify
the validity of our method \fxnote{WRITE BRIEF SUMMARY IN APPENDIX?}.
In the simulation, we can observe the high heating rate due to the high LD parameters
and confirm that by using high order Raman sideband transition in the cooling sequence we can
suppress this effect and reduces the motional energy of the atom faster.
The simulation is also used to guide the optimization of the cooling sequence by exploring the
large parameter space and finding a robust cooling strategy.
As shown in figure \ref{f-setup}C, we found that instead of cooling on only one sideband order
at a time, it is generally more efficient to alternate the cooling pulse between two
neighboring orders (axial) to minimize the accumulation of atom in a state
not addressed by a particular order.
The simulation also shows that an efficient way of cooling on a high order sideband is
to set the Rabi frequency of the Raman transition to perform a $\pi$ pulse for the maximum matrix element of that order over all states (i.e. the maxima in \ref{f-ld}A).
This makes sure we are using each order to cool a range of states that has the strongest
coupling to this order and let other sidebands to cool other states.

The efficiency of this approach diminishes during the last stages of cooling as the atom approaches the ground state.  We therefore finish the sequence by cooling only on the first order sideband while maintaining the alternating order between different axes.
Guided by the simulation results, we construct our initial cooling sequence by first starting
at the highest two observed cooling sideband and decrease the order after cooling on them
for 6 to 15 cycles with the optimum pulse lengths.
This sequence gives good cooling performance which is then experimentally further optimized
by fine tuning of different parameters.

For the more tightly confined radial directions,
we begin the cooling with $\{\bar n_2, \bar n_3\}=3.4(2), 2.5(2)$.
The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
as orange and red lines, where we can clearly see the first order heating,
first order cooling and second order cooling sidebands.
After applying around 1000 cooling pulses cooling in all three dimensions
starting with cooling on the radial second order,
the Raman spectrum with the same parameters is shown in figure \ref{f-radial}A as
blue and green lines, where the first and second order cooling sidebands
on both axis are suppressed.
Given the absence of the second order cooling sideband,
we can estimate the ground state probability in each direction based on the height of
the first order cooling and heating sideband to be $90(2)\%$ and $94(3)\%$.

It is important to note that the large Raman LD parameters $\eta^R$ mean that
we must use caution when measuring the temperature.
Traditional sideband thermometry uses
the ratio of the cooling and heating sidebands to measure $\bar n / (\bar n + 1)$, which relies
on the coupling strength to be proportional to $\sqrt{n}$. However, outside the
LD regime, the coupling strength deviates from this simple scaling rule rapidly as
shown in figure \ref{f-ld}A.
When the atom temperature is still high,
we measure the heights of multiple sidebands to make sure no population is hidden at the
minimum of one sideband order. Once the atom is cooled down, we estimate the temperature
and ground state population under the assumption that only a few states are populated.
We can verify the result via an independent measurement of Rabi flopping on the carrier and heating
sidebands. This data is shown before and after cooling in Figures
\ref{f-radial}B and \ref{f-radial}C and yields $89(2)\%$ and $92(2)\%$
showing good agreement between the two methods.

The axial direction is much less confined and therefore has a much higher initial effective
LD parameter of $\eta^{OP}_{eff1}\approx 4.0$, and is therefore more difficult to cool.
The red line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
before applying Raman sideband cooling; the clearly resolved sidebands
up to eighth order indicates population in highly-excited motional levels.
Therefore, we begin our cooling sequence by driving Raman transitions on the eighth order axial
cooling sideband. After applying the cooling sequence identical to the one we use to cool
the radial directions, the spectrum is shown in figure \ref{f-axial}A as the blue line.
All of the high order ($\geqslant2$) axial cooling sidebands disappear, and the first order
cooling sideband is strongly suppressed.
The ground state probability calculated from this spectrum is $92(3)\%$.
We can again use Rabi flopping on the carrier and heating sideband to verify this result
similar to the radial direction. In this case, we see very good agreement on the carrier
(figure \ref{f-axial}B) but there is additional decoherence on the axial first order
heating sideband (figure \ref{f-axial}C).
We believe this decoherence is caused by technical noise, which is the most pronounced
on this transition due to its slow Rabi frequency.
The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG that we have measured in the lab, which produces
a Zeeman shift of around $3$ kHz.
